---
title: "Single Cell RNA-seq Cell-Cell Interaction Analysis"
author: "Zain Arifin"
date: "2022-08-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(Seurat)
library(magrittr)
library(liana)
```


Liana (a LIgand-receptor ANalysis frAmework) is a cell-cell interaction method that compiles various cell-cell interaction methods, including:

1. CellPhoneDBv2 (*, $)

2. CellChat

3. NATMI (*, $)

4. Connectome (edge_weights) (*, $)

5. SingleCellSignalR (LRscores) (SCA) (*, $)

6. iTALK-inspired 1-vs-rest LogFC score (logfc_comb) (*, $)

7. CytoTalk-inspired cross-talk scores (*)

8. consensus_rank of the predictions is also provided using the RobustRankAggregate package

*The scoring systems from these methods were re-implemented in LIANA in order to account for multimeric complexes, simplify the calls to the individual pipelines, or reduce any possible inconsistencies and redundancies in their downstream integration. 

$ Default methods in LIANA.

liana takes Seurat and SingleCellExperiment objects as input, containing processed counts and clustered cells.

```{r data-input}
#Humand PBMC from SeuratData
#example data is normalized but not scaled

liana_path <- system.file(package = "liana")
testdata <-
  readRDS(file.path(liana_path , "testdata", "input", "testdata.rds"))

testdata <- SetIdent(testdata, value = testdata@meta.data$seurat_annotations)
```

```{r run-Liana}
# Run liana
liana_test <- liana_wrap(testdata)

# Liana returns a list of results, each element of which corresponds to a method
liana_test %>% dplyr::glimpse()

liana_test <- liana_test %>%
  liana_aggregate() #*

# (*) The aggregate consensus rank (aggregate_rank) is obtained using a re-implementation of the RRA method from the RobustRankAggreg package.
# 
# RRA scores can be interpreted as p-values and interactions which are ranked consistently higher than random are assigned low scores/p-values.
```

Visualizatio of interaction from B cell to other lymphocites

```{r}
liana_trunc <- liana_test %>%
   # only keep interactions concordant between methods
  filter(aggregate_rank <= 0.01) # this can be FDR-corr if n is too high

liana_trunc %>%
  liana_dotplot(source_groups = c("B"),
                target_groups = c("NK", "CD8 T", "B"),
                ntop = 30)
if(!require("circlize")){
  install.packages("circlize", quiet = TRUE,
                   repos = "http://cran.us.r-project.org")
}

p <- chord_freq(liana_trunc,
                source_groups = c("CD8 T", "NK", "B"),
                target_groups = c("CD8 T", "NK", "B"))

```

