---
title: "Single Cell RNA-seq Cell Type Annotation with PBMC Multimodal Reference (Seurat)"
author: "Zain Arifin"
date: "2022-08-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Seurat)
library(SeuratDisk)
library(tidyverse)
library(patchwork)
library(SeuratData)
```

## Load Reference

The refererence can be downloaded through: https://atlas.fredhutch.org/data/nygc/multimodal/pbmc_multimodal.h5seurat

The reference file is 2 Gb in size. It is advised to not run this script if you have insufficient RAM.

```{r}
reference <- LoadH5Seurat("pbmc_multimodal.h5seurat")
DimPlot(object = reference, reduction = "wnn.umap", group.by = "celltype.l2", 
        label = TRUE, label.size = 3, repel = TRUE) + NoLegend()
```

## Preprocessing with scTransform

Since the reference file was processed with scTransform, it is advised to also process the query with scTransform (even though other method pre-processing also works).

## Preprocess and Integration

```{r preprocess, warning=F}
InstallData("ifnb")
LoadData("ifnb")

ifnb.list <- SplitObject(ifnb, split.by = "stim")

for (i in 1:length(ifnb.list)){
  ifnb.list[[i]] <- SCTransform(ifnb.list[[i]], vst.flavor = "v2", verbose = FALSE) %>%
    RunPCA(npcs = 30, verbose = FALSE) %>%
    RunUMAP(reduction = "pca", dims = 1:30, verbose = FALSE) %>%
    FindNeighbors(reduction = "pca", dims = 1:30, verbose = FALSE) %>%
    FindClusters(resolution = 0.7, verbose = FALSE)
}

features <- SelectIntegrationFeatures(object.list = ifnb.list, nfeatures = 3000)
ifnb.list <- PrepSCTIntegration(object.list = ifnb.list, anchor.features = features)

immune.anchors <- FindIntegrationAnchors(object.list = ifnb.list, normalization.method = "SCT",
    anchor.features = features)
immune.combined.sct <- IntegrateData(anchorset = immune.anchors, normalization.method = "SCT")

immune.combined.sct <- RunPCA(immune.combined.sct, verbose = FALSE)
immune.combined.sct <- RunUMAP(immune.combined.sct, reduction = "pca", dims = 1:30, verbose = FALSE)
immune.combined.sct <- FindNeighbors(immune.combined.sct, reduction = "pca", dims = 1:30)
immune.combined.sct <- FindClusters(immune.combined.sct, resolution = 2)
```

```{r}
ref_anchors <- FindTransferAnchors(
  reference = reference,
  query = immune.combined.sct,
  normalization.method = "SCT",
  reference.reduction = "pca",
  dims = 1:30
)

immune.combined.sct <- MapQuery(
  anchorset = ref_anchors,
  query = immune.combined.sct,
  reference = reference,
  refdata = list(
    celltype.l1 = "celltype.l1",
    celltype.l2 = "celltype.l2",
    predicted_ADT = "ADT"
  ),
  reference.reduction = "pca"
)
```

## VIZ

```{r}
p1 <- DimPlot(immune.combined.sct, group.by = "seurat_annotations", label = T)
p2 <- DimPlot(immune.combined.sct, group.by = "predicted.celltype.l1", label = T)
p3 <- DimPlot(immune.combined.sct, group.by = "predicted.celltype.l2", label = T)

p1
p2
p3
```


```{r}
meta <- immune.combined.sct@meta.data

celltype_summary <- meta %>%
  group_by(seurat_clusters) %>%
  count(predicted.celltype.l2) %>%
  slice(which.max(n)) %>%
  ungroup()
celltype_summary <- celltype_summary %>% dplyr::select(-n)
names(celltype_summary)[2] <- "l2_Cluster"

meta <- left_join(meta, celltype_summary)
immune.combined.sct@meta.data$l2_Cluster <- meta$l2_Cluster

p4 <- DimPlot(immune.combined.sct, group.by = "l2_Cluster", label = T, repel = T)
p4
p1
```

